\documentclass[line,margin]{res} 
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, filecolor=magenta, urlcolor=blue}
\newcommand{\goodtilde}{\raise.17ex\hbox{$\scriptstyle\mathtt{\sim}$}}
\newsectionwidth{90pt}
\sectionskip9pt
\parskip7pt
\begin{document}

\name{Adam Zethraeus}
\address{adam@zethrae.us}
\address{+1 (401) 339-8675}

 
\begin{resume}

\section{SKILLSET}
    {\sl Active use:} iOS: Swift, RxSwift, Cocoa. Technical leadership \& Communication. \\
    {\sl Familar tools:} Objective-C, Java, Python, Go, C++, JavaScript.

\section{EXPERIENCE}
    \textbf{Uber — Sr. 2 Mobile Tech Lead \& Architect} \hfill \textbf{07/2015—Present}

    {\sl Uber: New Mobility} (Bikes, Scooters, 3rd party micromobility) \hfill {\sl07/2018—Present}
    \begin{itemize}  \itemsep -1pt
        \item Led mobile launches for, and owned health of, products which supported (on the order of magnitude of) a hundred cities and a million rides/week at peak. Launched \href{https://www.uber.com/newsroom/jump-scooters/}{JUMP Scooters}, \href{https://www.theverge.com/2018/7/9/17548848/uber-investment-lime-scooter-alphabet}{3rd party Lime Scooters}, and \href{https://www.uber.com/newsroom/cityscoot-emopeds/}{3rd party Cityscoot mopeds in the EU}.
        \item Responsible for establishing and maintaining rigorous engineering, oncall, metrics/data-science, and monitoring practices within the \goodtilde40 engineer bike/scooter group.
        \item Spearheaded and led a reactive programming (RxSwift/RxJava) based mobile rearchitecture which improved app responsiveness (by enabling state update pushes from the backend) and startup times (p90: 7 seconds $\rightarrow$ 400 milliseconds).
        \item Led the cross-org effort to integrate Uber's micromobility offerings into the app's main entrypoints (\href{https://techcrunch.com/2019/07/01/uber-brings-bikes-and-scooters-including-limes-to-the-forefront/}{example}), lifting first trips by \goodtilde20\%.
        \item Designed, evangelized, and spearheaded an API redesign to facilitate 3rd party micromobility integrations. This extensible contract decreased the cost of development for new vehicle types and partnerships.
        \item Co-Architected the self-standing \href{https://apps.apple.com/us/app/jump-by-uber/id1251322970}{JUMP 2.0} and \href{https://www.jump.com/us/en/jumpstarter/how-it-works/}{JUMPStarter} contractor apps.
    \end{itemize}

    {\sl Uber: Mobile Platform, iOS} \hfill {\sl01/2017—06/2018} \\ 
    I fostered and guarded the architecture and code health across all of Uber's mobile presence and business lines.
    My responsibilities and initiatives included migrating business critical infrastructure, code reviewing the most fragile app changes, designing a shim layer supporting Uber's new Swift based \href{https://github.com/uber/RIBs}{RIB} architecture, improving experiment reliability, driving down Rider app startup time, and building out Uber's mobile training sessions.

    {\sl Uber: Driver Organization, iOS} \hfill {\sl07/2015—12/2016} \\
    Led Driver Profiles mobile feature team. Earlier: Driver growth \& referrals.

    \textbf{Sparks} (Greylock seed funded), {\sl Fullstack Engineer} \hfill \textbf{05/2014—06/2015} \\
    iOS and Python/Flask/EC2 engineering for Apple and Facebook featured social apps.

    \textbf{Amazon AWS} {\sl Web Browser Engineer} \hfill \textbf{09/2012—02/2014} \\
    I worked on the C++/Chromium \href{https://chromium.googlesource.com/chromium/src/+/HEAD/content/public/README.md}{Content API} layer of \href{https://en.wikipedia.org/wiki/Amazon_Silk}{Amazon Silk}, building an enhanced Android WebView and owning implementation of interfaces for then unexposed Chromium functionality including incognito profiles, prerendering, and resource prefetching.

\section{EDUCATION}
    \textbf{Brown University} {\sl A.B. Computer Science} \hfill 2008—2012 \\
    {\sl CS lead TA / Course Designer:} CS4 (Scientific Computing), CS 132 (Web Development)
    {\sl Further TA work:} CS15 (Intro to OOP), CS31 (Systems), CS180 (Cybersecurity Policy)\\
    {\sl Extracurricular:} Varsity Fencing

\section{PERSONAL NOTES}
    Fluent in Swedish \& English. Swedish \& US citizen.\\
    Passions: Neon artist, avid skiier, long distance runner. \\
    Free time: Reading (founded and run a Tech/Business book club) and learning beyond my day job (e.g. Andrew Ng's machine learning course, computer graphics, programming languages, and currently: quantum mechanics/computing fundamentals.)

\end{resume}
\end{document}
